---
title: "Lab 6 Comparing Two Means"
author: "Hiba Chaudhry"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


Researchers studying the number of electric fish species living in various parts of the Amazon basin were interested in whether the presence of tributaries affected the local number of electric fish species in the main rivers (Fernandes et al. 2004).

They counted the number of electric fish species above and below the entrance point of a major tributary at 12 different river locations.

The data is provided in your GitHub repository.

For each question below, write a sentence answering the question and show the code you used to come up with the answer, if applicable. like this:


```{r}
library(tidyverse)

fish <- read_csv("chap12q19ElectricFish.csv")


# put data in tidy format ------------------------------------------------

fish_long <- 
  pivot_longer(fish, speciesUpstream:speciesDownstream,
               names_to = "location",
               values_to = "species") %>% 
  mutate(location = str_remove(location, c("species"))) %>% 
  print()

```


## Question A

> Test the hypothesis that the tributaries have no effect on the number of species of electric fish.


```{r t-test}
fish_ttest <- t.test(species ~ location, data = fish_long)
fish_ttest$estimate
```

#Interpreting the t test:
  Mean of Downstream : 16.41667
  Mean of Upstream: 14.58333
  Difference is: 1.83334
  Standard deviation of both groups are not the same so it is not a two sample t test because the third assumption is violated 
  P-value is 0.5596, meaning that we fail to reject our null hypothesis 

ANSWER

## Question B

> What is the difference in the mean numbers of species between areas upstream and downstream of a tributary? What is the 95% confidence interval of this difference in means?

ANSWER

```{r}
fish_mean_diff <-
  fish_long %>% 
  group_by(location) %>% 
  summarize(
    n = n(),
    mean = mean(species),
    sd = sd(species),
    sem = sd/sqrt(n),
    upper = mean + 1.96 * sem,
    lower = mean - 1.96 * sem
  ) %>% 
  print()
```


## Question C

> State the assumptions that you had to make to complete parts (A) and (B). Create a graph to assess whether one of those assumptions was met.

ANSWER

```{r}
fish_long %>%
    ggplot(aes(x = species)) +
    geom_histogram(
    aes(fill = location), 
    bins = 5, 
    alpha = 0.5, 
    position = "identity"
    ) 
```


## Question D

> Graph the distribution of body temperatures for each crab type:

ANSWER

```{r}
crabs <- read_csv("chap15q27FiddlerCrabFans.txt")
crabs

# D) 
crabs %>%
  ggplot(aes(x = bodyTemperature)) +
  geom_histogram(
    aes(fill = crabType ), 
    bins = 5, 
    alpha = 0.5, 
    position = "identity"
  ) +
  facet_wrap(~ crabType)
```


## Question E

> Does body temperature varies among crab types? State the null and alternative hypothesis, conduct and ANOVA, and interpret the results.

ANSWER 

```{r}
aov_crabs <- 
  aov(bodyTemperature ~ crabType, data = crabs)
aov_crabs

summary(aov_crabs)
```

# H0: Body temperature is equal among all crab types
# HA: At least one crab type will be different from the others 


#Interpreting the ANOVA
  Mean of crabType: .8804
  Mean of Residuals: .0433
  P-value: .0000000007. It is smaller than 0.5 so we reject our null hypothesis 
